### 2020-06-07 ms/ms.tex
Incorporate Geir's and Brian's suggestions

Despite the overall decreases in marine survival,
the conservation status of Canadian salmon populations differ
considerably. In Canada, populations in the southern part of their range are more
likely to be assessed as being of conservation concern than those in more
northerly regions \citep{Cosewic2010}. This latitudinal disparity in status
suggests that if marine survival has been, or is, a key factor responsible for
most population declines, these changes are not uniformly distributed across
all populations.

@@

Smolt and adult return abundance estimates originate from a variety of
sources. Smolt estimates from the Trinit\'{e}, Saint-Jean, LaHave, Nashwaak,
and Conne populations were obtained using a mark-recapture approach, while
estimates from the WAB and Campbellton populations were obtained by direct
counts using fish counting fences.
For further details on the data collection methodologies refer to 
\citet{Dempson1991, Venoitt2018} for NL populations, 
\citet{April2018}  for QC populations,
\citet{Jones2014} for NB population,
and \citet{Gibson2009} for NS population.

@@

where $p_{r,t,a}$ is the proportion of annual returns in river $r$, year $t$,
and of spawning history $a$ (either 1SW or 2SW returns); $n_{r,t,s,a}$ is the
number of samples in river $r$, year $t$, of returning age $a$, and of size
group $s$; $n_{r,t,s}$ is the total number of samples in river $r$, year $t$,
and of size group $s$; and $N_{r,t,s}$ is the returns of salmon
in river $r$, year $t$, and of size group $s$.
While, ideally, we would account the uncertainty in the conversion between
size group and returning age, this is being ignored by doing this conversion
deterministically as shown above. However, sampling a parameter from a
hypergeometric distribution is not possible in programming the model was
written in (i.e. Stan).

@@

where $smolts_{true,t,r}$ are the true smolt abundances for year $t$ and river
$r$, and $\epsilon_{t,r}$ is the error term, which is calculated from the yearly 
coefficient of variation in the empirically derived
smolt estimates (see Tables S1 and S2 in the Supplementary material). 
Where available, we used population-specific measurement error estimates for smolt abundances; if not 
available, we set measurement error between 5 and 10\%. 
The log-transformed true smolt abundances are
normally distributed around a population-level mean and standard deviation:

@@

These error terms are almost equivalent to using a coefficient of variation in
return estimates 1\%, given that return estimates in equations~\ref{eq:3}
and~\ref{eq:4} are log-transformed. As
there is no associated uncertainty with most return estimates, we chose this value arbitrarily
based on the expectation that uncertainty in returns estimates is likely lower than in
smolt estimates.

@@

These priors, when converted to yearly survival, are roughly constrained between
0 and 0.2 for \So and between 0.2 and 0.5 for \St (Fig.~\ref{fig:priors}a). They are
informative only to the extent that they limit the estimates of marine survival
to what what we considered to be biologically realistic.

@@

The three Newfoundland populations (WAB, Campbellton and Conne) are considered to be 
1SW-dominated, while the other four have the more generic priors for $logit(P_{g,t})$.
These priors, when converted back to a proportion, are narrowly constrained
for 1SW-dominated populations, but relatively wide for all other populations
(Fig.~\ref{fig:priors}b).

@@

Trends in estimates of marine survival in the first winter at sea (\So) were 
highly variable within and among populations
(Fig.~\ref{fig:s1-dual}). The highest median posterior estimates of \So
were for the Nashwaak River in 2006 and 2008, with values of 0.18 and 0.21,
respectively. The lowest median \So estimate was in the Trinit\'{e} in 2001,
with an estimate of \So of 0.007, while the Conne, LaHave, and Trinit\'{e} had
years where estimates of \So varied between 0.01 and 0.02 (Fig.~\ref{fig:s1-faceted}).

Trends among populations also varied: Campbellton,
Saint-Jean, and Western Arm Brook populations showed increases in \So
over time, Trinit\'{e}, Conne, and LaHave populations showed decreases,
while at Nashwaak there was an increase in median \So during the early
2000s but a decrease in the 2010s. Yearly estimates of \So had very little
variability for one sea-winter dominated populations (Conne, Campbellton, and
WAB), but were more variable (i.e. wider credible intervals) in the other
populations.

\begin{figure}[htbp] \centering
    \includegraphics[width=0.95\linewidth]{figures/s1-trends-dual.png}
    \caption{Trends in survival in the first year at sea (\So). a) Posterior
        estimates of \So for the seven populations examined, error bars indicate
        the 90\% credible intervals, and dashed lines denote years of commercial
        fishing moratoria for each province. b) Z-scores of median posterior
        estimates.} \label{fig:s1-dual} \end{figure}

\begin{figure}[htbp] \centering
    \includegraphics[width=0.95\linewidth]{figures/s1-trends-faceted.png}
    \caption{Posterior estimates of \So for the seven populations examined, error
        bars indicate the 90\% credible intervals.} \label{fig:s1-faceted}
\end{figure}

Estimates of \St were highly uncertain in all populations, and trends 
were not apparent in most populations given the large range of the credible
intervals in the yearly estimates (Fig.~\ref{fig:s2-faceted}). The estimates
of \St for the Saint-Jean and Trinit\'{e} were considerably less uncertain
than for the other populations, but showed no apparent trends through time.

\begin{figure}[htbp] \centering
    \includegraphics[width=0.95\linewidth]{figures/s2-trends-faceted.png}
    \caption{Posterior estimates of \St for the seven populations examined, error
        bars indicate the 90\% credible intervals.} \label{fig:s2-faceted}
\end{figure}

@@

\begin{figure}[htbp] \centering
    \includegraphics[width=0.95\linewidth]{figures/pr-trends-faceted.png}
    \caption{Posterior estimates of \Pg for the seven populations examined, error
        bars indicate the 90\% credible intervals. Year corresponds to the
        year of 1SW return.} \label{fig:pr-faceted} 
\end{figure}

Population-level estimates of \prmu and \prsig varied considerably among populations. For all
three 1SW-dominated populations (Campbellton, Conne, and WAB), estimates of \prmu
were very close to 1.0 and had little variability in \prsig (Fig~\ref{fig:prmu-post}; Table~\ref{tab:prmu}).
Estimates of \prmu were the lowest for the two QC populations, particularly the Saint-Jean (median \prmu = 0.11).
Estimates of \prmu for the Nashwaak and the LaHave populations were close to 0.5, with these two populations having 
the highest estimated values of \prsig, particularly the Nashwaak (Fig~\ref{fig:prmu-post}; Table~\ref{tab:prsigma}).

\input{table-logitprmu.tex}

\input{table-logitprsigma.tex}

@@

As is expected from Murphy's method, there is a strong negative correlation
between survival in the second year at sea (i.e. $-Z_2$) and proportion returning
as 1SW ($log(P_g)$, Fig.~\ref{fig:cor-params}). Some populations (Campbellton,
LaHave, Nashwaak, and Saint-Jean) show a negative correlation between the
estimated number of smolts and survival in the first year at sea, while the
others fluctuate around zero. There is overall a positive correlation between
survival in the first year (i.e. $-Z_1$) and proportion returning as 1SW,
except for the Campbellton, where this correlation is negative.

\begin{figure}[htbp] \centering
    \includegraphics[width=0.95\linewidth]{figures/corrected-cor-ALL.png}
    \caption{Estimated correlations among estimated model parameters.}
    \label{fig:cor-params} 
\end{figure}

Overall, variation in return abundances was mostly explained by marine survival in the
first winter at sea, with $R^2$ estimates between 0.5 and 0.75 for all populations
with the exception of the Saint-Jean (Fig.~\ref{fig:mu-rsq}).
The low $R^2$ for the Saint-Jean is likely due to the negative correlation
between survival and number of outmigrating smolts (Fig.~\ref{fig:cor-params}). 
Populations with a lower proportion of 1SW in their returns (e.g. Trinit\'{e}
and Saint-Jean) have a higher $R^2$ with estimated number of smolts than those
that are 1SW-dominated, but overall, smolts estimates had low $R^2$ values in 
all populations except the Saint-Jean (Fig.~\ref{fig:mu-rsq}).
The proportion returning as 1SW explained a moderate amount of the variance in
estimated 1SW returns in the Conne, LaHave, and Nashwaak, and much less in the
other four populations.

Values of $R^2$ were overall low for all parameters with regards to explaining
the variance of estimated 2SW returns. Estimates of survival in the second winter at sea ($Z_2$)
explained little variance in estimates for 2SW returns, with the Saint-Jean again being the
exception.

@@

% Our results challenge the narrative that marine survival, specifically
% survival in the first year at sea, is declining uniformly throughout the
% range of Atlantic salmon in the northwest Atlantic.
Our results indicate that trends in marine survival among Atlantic salmon
populations in eastern Canada are highly variable, both temporally and
spatially. Over the time periods for which data were available, some
populations show positive trends in survival in the first winter at sea (\So)
while other exhibit highly variable yet stable trends, and some show declines.
We could not assess trends in the second winter at sea (\St) or proportion
returning as grilse (\Pg), as these parameter estimates were highly uncertain
and were strongly influenced by the priors. Perhaps there is a need to rethink
our understanding of Atlantic salmon population dynamics in light of the
possibilities that (1) any real and persistent declines in marine survival
have been experienced by some but not necessarily all populations, (2)
reductions in survival might have occurred over a relatively brief period of
time and have not persisted, (3) marine survival has been relatively stable,
or increasing in some populations for one or more decades, (4) variation in
survival at the population level can be large even within a region.

% 2. How they compare to other publications
% Population vs regional trends

Interestingly, our estimates of both \So and \St for the Trinit\'{e}
population are very similar to those produced by \citet{Chaput2003b} using a
two sex model, and our trends are almost identical for the overlapping time
period that marine survival was estimated for in their study (1984-1998). 
While \citet{Chaput2003b} separated abundance data for males and females
based on sex ratio information and assumed their survival rates were the 
same (to be able to reach an analytical solution), our study reached almost the same results (albeit with
slightly higher uncertainty), using a Bayesian approach with informative
priors. These overlapping trends obtained with two different methods 
suggest that our method is indeed effective at estimating marine survival.

Trends in marine survival
among populations were compared by \citet{Chaput2012a} using adult return rates.
He found that for 4 of 6 populations examined, return rates in the 1990s 
were lower than those during the 1970s.
\citet{Gibson2016} calculated higher return rates of 2SW for the Nashwaak in
the 1970s than in the period since, with return rates of 1SW in the 1970s
being comparable to those in the late 2000s.
\citet{Friedland1993} compared return rates for a number of populations in eastern
North America between 1973 and 1988, and suggested there are similar trends among these. 
However, the similarity in these trends was driven primarily by two years, 1977 and 1978, which
show concurrent low and high relative return rates across populations,
respectively. Other years are much more variable relative to each other.
\citeauthor{Friedland1993}'s \citeyear{Friedland1993} time series ends in  
1988; thus there are only a few years for which to assess overlap with the
time series in our study.
While declines in return rates since the 1970s seem to be consistent among populations, 
we were unable to assess if marine survival estimates were also higher in the 1970s as we lacked 
data from this decade.

In any event, we caution that the pooling of adult return rates
\citep{Chaput2012a, Friedland1993,Gibson2016} can mask inter-annual
variability in marine survival \citep{Hubley2011}, and hence might not produce
an accurate depiction of marine survival trends.
While river-specific return rate estimates are available for the populations
used in this study \citep{ICES2019}, these estimates are only an approximation
of marine survival with varying degrees of similarity depending on each
population's life histories. The estimates of return rates of one sea-winter
approximate marine survival in the first year at sea for one
sea-winter-dominated populations, and we see this by comparing the three NL populations
with the return rates presented in \citet{ICES2019}. However, as the proportion of fish that
return as one sea-winter decreases, marine survival in the first year at sea
can increasingly diverge from return rates of fish, and trends in return rate
would be particularly misleading if the proportion returning as one sea-winter
varies in time. 
Furthermore, return rates of two sea-winter fish also include survival in the
first winter at sea and the proportion returning as two sea-winter, thus
providing a very coarse estimate of marine survival in the second year at sea. 
As changes in return rates of two sea-winter fish are a result of a
combination of changes in survival in the first year at sea in the year prior,
survival in the second year at sea, and in the proportion returning as two
sea-winter, an increase in any of those parameters while the others remain
the same will result in an increase in return rates. Our model attempts to
improve some of the shortcomings of using return rates as a proxy of marine
survival by directly estimating marine survival in the first and second years
at sea, as well as the proportion returning as 1SW.

\citet{Dempson2003} described a general declining trend in marine survival for
Newfoundland populations (except WAB); we drew the same conclusion for 
Conne River but not Campbellton River or WAB. It is not possible to draw broader conclusions
with data from only three Newfoundland populations, but it seems that among index rivers,
those in Newfoundland are among those with the highest marine survival rates.

At first glance, the large variation in marine survival trends among the seven
populations examined in our study seems to be at odds with the synchronous
trends of declining marine survival detected at broad regional scales
\citep{Olmos2019}. However, these two observations are not necessarily mutually
exclusive: our study is only a small subsample of the populations in the region,
and highly variable trends in marine survival among populations can still add
up to overall negative trends at a regional scale.
Aside from the overarching difference in the spatial scale of data sources
(i.e. river vs province scales), the divergence in local versus regional
trends could be further confounded by differences in model structure, such as
the methodology for estimating covariance, and use stock-recruitment
relationships rather than empirical smolt count estimates to estimate marine
survival.
% As trends in marine survival during the first winter at sea are highly
% independent among rivers on relatively small spatial scale, 
Our results suggest that trends from broader geographical areas (i.e.
province, state, or country-wide estimates) may not be representative of
individual populations, and concomitantly, trends of individual populations
may also not be representative of region-wide trends.

% 3. Potential reasons
There are a variety of potential explanations for the highly variable trends
in estimates marine survival in the first winter at sea.
Environmental drivers of survival (e.g., temperature, predation, prey abundance) 
could be local environmental drivers
relative to broader-scale, even ocean-wide, drivers.
A recent study showed that correlations between oceanic temperature, primary
productivity, and post smolt survival of Atlantic salmon in the North Atlantic
are better explained by broad-scale environmental trends than regional ones
\citep{Olmos2020}.
However these local drivers are potentially much more difficult to quantify than 
broader ones.
% The synchrony reported for marine survival trends at broader spatial 
% scales \citep{Massiot-Granier2014,Olmos2019} might be attributable to the 
% use of stock-recruitment relationships to estimate survival,
% relationships that may have been confounded by changes in recruitment dynamics.
There is some evidence of a correlation between return rate and growth (as
indicated by inter-circuli spacing on scales), where years of poor growth
tended to also be years of poor survival \citep{Friedland1993}, supporting the
idea that marine survival is mediated by environmentally-driven changes in growth.
Furthermore, among European salmon, there is evidence of a positive correlation
between spring temperature in the Norwegian and North Seas and population abundance, 
suggesting warmer
conditions favour post-smolts \citep{Friedland1998}, based on mapping the
extent of area of suitable temperature (7-13 \textdegree C).

@@

While there is little evidence that marine survival is density-dependent in
Atlantic salmon \citep{Jonsson1998,Gibson2006}, there could potentially be
some density-dependent processes during parts of the marine phase, 
particularly for populations that are likely to be subjected to
declining per capita population growth rates ($r$) generated by Allee effects.
Exploring relationships between survival and population size could potentially
shed light about the processes that have caused many of the population
declines that have been documented.

@@

Egg-to-smolt survival in Atlantic salmon is highly variable
\citep{Klemetsen2003,Chaput2015}.
While this variability is likely attributable to changes in freshwater
conditions (e.g. discharge, temperature, water quality) and uncertainty in
spawner and smolt estimates, 
changes in the oceanic conditions that spawners experience could also be
contributing to this variability.

Obviously, there would be a time lag (perhaps as much as a generation) in how such effects
might be manifest at the adult stage.
However, given that most correlations are between relatively monotonic declines
in abundance coupled also monotonic increases in climatic indices
over decadal time scales \citep[e.g.,][]{Friedland1998, Todd2008,
    Beaugrand2012}, it would be expected that these correlations would be
maintained even if salmon abundances were lagged by a generation length.

@@

Secondly, the assumed hierarchical structure might not be the most appropriate
for modelling smolt abundances. This approach results in shrinkage to the
mean, which means that the variability of annual smolt estimates is less than
it would be if not modelled hierarchically. 
That said, this assumption is likely to result in more conservative trends in
marine survival, as the variation is smolt estimates is reduced.
This shrinkage of annual smolt abundances is also reducing the $R^2$ values 
between smolts and estimates returns, albeit only marginally.
It is important to note that the hierarchical structure in the estimation of
\Pg seems like a reasonable assumption given that the probability of returning
as grilse has a genetic component associated to it \citep{Aykanat2019} and is
not expected to vary much, within a population, among years.

>>>>

Despite the overall decreases in marine survival,
the conservation status of Canadian salmon populations differs
considerably. In Canada, populations in the southern part of their range are more
likely to be assessed as being of conservation concern than those in more
northerly regions \citep{Cosewic2010}. This latitudinal disparity in status
suggests that if marine survival has been, or is, a key factor responsible for
most population declines, these changes are not uniformly distributed across
all populations.

@@

Smolt and adult return abundance estimates originate from a variety of
sources. Smolt estimates from the Trinit\'{e}, Saint-Jean, LaHave, Nashwaak,
and Conne populations were obtained using a mark-recapture approach, while
estimates from the WAB and Campbellton populations were obtained by direct
counts using fish counting fences.
For further details on the data collection methodologies refer to 
\citet{Dempson1991}, \citet{Schwarz1994}, and \citet{Venoitt2018} for NL populations, 
\citet{April2018}  for QC populations,
\citet{Jones2014} for NB population,
and \citet{Gibson2009} for NS population.

@@

where $p_{r,t,a}$ is the proportion of annual returns in river $r$, year $t$,
and of spawning history $a$ (either 1SW or 2SW returns); $n_{r,t,s,a}$ is the
number of samples in river $r$, year $t$, of returning age $a$, and of size
group $s$; $n_{r,t,s}$ is the total number of samples in river $r$, year $t$,
and of size group $s$; and $N_{r,t,s}$ is the returns of salmon
in river $r$, year $t$, and of size group $s$.
While, ideally, we would account the uncertainty in the conversion between
size group and returning age, this is being ignored by doing this conversion
deterministically as shown above. However, sampling a parameter from a
hypergeometric distribution is not possible in the programming language the model was
written (i.e. Stan).

@@

where $smolts_{true,t,r}$ are the true smolt abundances for year $t$ and river
$r$, and $\epsilon_{t,r}$ is the error term, which is calculated from the yearly 
coefficient of variation in the empirically derived
smolt estimates (see Table S1 in the Supplementary material). 
Where available, we used population-specific measurement error estimates for smolt abundances; if not 
available, we set measurement error between 5 and 10\% (see Table S2 in the Supplementary material). 
The log-transformed true smolt abundances are
normally distributed around a population-level mean and standard deviation:

@@

These error terms are almost equivalent to using a coefficient of variation in
return estimates of 1\%, given that return estimates in equations~\ref{eq:3}
and~\ref{eq:4} are log-transformed. As
there is no associated uncertainty with most return estimates, we chose this value arbitrarily
based on the expectation that uncertainty in returns estimates is likely lower than in
smolt estimates.

@@

These priors, when converted to yearly survival, are roughly constrained between
0 and 0.2 for \So and between 0.2 and 0.5 for \St (Fig.~\ref{fig:priors}a). They are
informative only to the extent that they limit the estimates of marine survival
to what we considered to be biologically realistic.

@@

The three Newfoundland populations (WAB, Campbellton and Conne) are 
1SW-dominated, while the other four have the more generic priors for $logit(P_{g,t})$.
These priors, when converted back to a proportion, are narrowly constrained
for 1SW-dominated populations, but relatively wide for all other populations
(Fig.~\ref{fig:priors}b).

@@

Estimates of marine survival probabilities in the first winter at sea (\So) were 
highly variable within and among populations
(Fig.~\ref{fig:s1-dual}). The highest median posterior estimates of \So
were for the Nashwaak River in 2006 and 2008, with values of 0.18 and 0.21,
respectively. The lowest median \So estimate was in the Trinit\'{e} in 2001,
with an estimate of \So of 0.007, while the Conne, LaHave, and Trinit\'{e} had
years where the lowest estimates of \So varied between 0.01 and 0.02 (Fig.~\ref{fig:s1-faceted}).

Long-term trends among populations also varied: Campbellton,
Saint-Jean, and Western Arm Brook populations showed increases in \So
over time, Trinit\'{e}, Conne, and LaHave populations showed decreases,
while at Nashwaak there was an increase in median \So during the early
2000s but a decrease in the 2010s. Annual estimates of \So had little
uncertainty for one sea-winter dominated populations (Conne, Campbellton, and
WAB), but uncertainty was higher (i.e. wider credible intervals) in the other
populations.

% % Dual plot of trends in S1
% \begin{figure}[htbp] \centering
%     \includegraphics[width=0.95\linewidth]{figures/s1-trends-dual.png}
%     \caption{Trends in survival in the first year at sea (\So). a) Posterior
%         estimates of \So for the seven populations examined, error bars indicate
%         the 90\% credible intervals, and dashed lines denote years of commercial
%         fishing moratoria for each province. b) Z-scores of median posterior
%         estimates.} \label{fig:s1-dual} 
% \end{figure}

% Single plot of trends in S1
\begin{figure}[htbp] \centering
    \includegraphics[width=0.95\linewidth]{figures/s1-trends-all.png}
    \caption{Median posterior estimates of survival in the first year at sea (\So) 
        for the seven populations examined.} \label{fig:s1-dual} 
\end{figure}

\begin{figure}[htbp] \centering
    \includegraphics[width=0.95\linewidth]{figures/s1-trends-faceted.png}
    \caption{Posterior estimates of survival probabilities in the first year at sea (\So). Dots indicate median estimates and error
        bars indicate the 90\% credible intervals. Dashes vertical lines reflect the year the commercial fishing moratoria were enacted
    in each province.} \label{fig:s1-faceted}
\end{figure}

Estimates of survival in the second year at sea (\St) were highly uncertain in all populations, and trends 
were not apparent in most populations given the large range of the credible
intervals in the yearly estimates (Fig.~\ref{fig:s2-faceted}). The estimates
of \St for the Saint-Jean and Trinit\'{e} were considerably less uncertain
than for the other populations, but showed no apparent trends through time.

\begin{figure}[htbp] \centering
    \includegraphics[width=0.95\linewidth]{figures/s2-trends-faceted.png}
    \caption{Posterior estimates of survival in the second yyear at sea (\St).
 Dots indicate median estimates and error bars indicate the 90\% credible
 intervals. Dashes vertical lines reflect the year the commercial fishing
 moratoria were enacted in each province.} \label{fig:s2-faceted}
\end{figure}

@@

\begin{figure}[htbp] \centering
    \includegraphics[width=0.95\linewidth]{figures/pr-trends-faceted.png}
    \caption{Posterior estimates of proportion returning after one winter at sea (\Pg).
 Dots indicate median estimates and error
        bars indicate the 90\% credible intervals. Dashes vertical lines reflect the year the commercial fishing moratoria were enacted
    in each province.} \label{fig:pr-faceted} 
\end{figure}

Estimates of the population-level mean (\prmu) and standard deviation (\prsig) of proportion returning after one year at sea varied considerably among populations. 
For all
three 1SW-dominated populations (Campbellton, Conne, and WAB), estimates of \prmu
were very close to 1.0 and had little variation in \prsig (Fig~\ref{fig:prmu-post}; Table S7 in the Supplementary Materials).
Estimates of \prmu were the lowest for the two QC populations, particularly the Saint-Jean (median \prmu = 0.11).
Estimates of \prmu for the Nashwaak and the LaHave populations were close to 0.5, with these two populations having 
the highest estimated values of \prsig, particularly the Nashwaak (Fig~\ref{fig:prmu-post};  Table S8 in the Supplementary Materials).

% \input{table-logitprmu.tex}

% \input{table-logitprsigma.tex}

@@

As is expected from Murphy's method, there is a strong negative correlation
between survival in the second year at sea (i.e. $-Z_2$) and proportion returning
as 1SW ($log(P_g)$, Fig.~\ref{fig:cor-params}). Some populations (Campbellton,
LaHave, Nashwaak, and Saint-Jean) show a negative correlation between the
estimated number of smolts and survival in the first year at sea, while the
others fluctuate around zero. There is overall a positive correlation between
survival in the first year (i.e. $-Z_1$) and proportion returning as 1SW,
except for the Campbellton population, where this correlation is negative.

\begin{figure}[htbp] \centering
    \includegraphics[width=0.95\linewidth]{figures/corrected-cor-ALL.png}
    \caption{Correlations among estimated model parameters. \emph{log(smolts)} = estimated smolt abundances in log-space, $log(P_g)$ = logit-transformed probability of
        returning after one year at sea, $-Z_1$ = marine survival in the first year at sea, and $-Z_2$ = marine survival in the second year at sea.
        Note the correlations derived from negative instantaneous total mortalities $-Z_1$ and $-Z_2$ are equivalent to those of marine survival $S_1$ and $S_2$.}
    \label{fig:cor-params} 
\end{figure}

Overall, variation in return abundances was mostly explained by marine survival in the
first winter at sea, with $R^2$ estimates between 0.5 and 0.75 for all populations
with the exception of the Saint-Jean (Fig.~\ref{fig:mu-rsq}).
The low $R^2$ for the Saint-Jean is likely due to the negative correlation
between survival (i.e. $-Z_1$) and number of outmigrating smolts (see Fig.~\ref{fig:cor-params}). 
There are also moderately negative correlations between survival and smolts in
the Campbellton, LaHave, and Nashwaak populations.
These negative correlations could be indicative of density-dependent
mortality at sea, however this is generally thought to be is unlikely.
Populations with a lower proportion of 1SW in their returns (e.g. Trinit\'{e}
and Saint-Jean) have a higher $R^2$ with estimated number of smolts than those
that are 1SW-dominated, but overall, smolts estimates had low $R^2$ values in 
all populations except the Saint-Jean (Fig.~\ref{fig:mu-rsq}).
The proportion returning as 1SW explained a moderate amount of the variance in
estimated 1SW returns in the Conne, LaHave, and Nashwaak, and much less in the
other four populations.
Values of $R^2$ were overall low for all parameters with regards to explaining
the variance of estimated 2SW returns. Estimates of mortality in the second winter at sea ($Z_2$)
explained little variance in estimates for 2SW returns, with the Saint-Jean again being the
exception.

@@

Our results show that trends in marine survival among monitored Atlantic salmon
populations in eastern Canada are highly variable, both temporally and
spatially. Over the time periods for which data were available, some
populations show positive trends in survival in the first winter at sea (\So)
while other exhibits highly variable yet stable trends, and some show declines.
Variation in survival at the population level can be large even within
a region, and there are no consistent declines in marine survival in any
population after the onset of fishing moratoria, except perhaps in the LaHave
River where the four last years in the time-series (2014-2017) had survival of
less than 2.5\%.
However, while correlations in marine survival trends between rivers were highly 
variable (Fig.~\ref{fig:s1-corr}),
there are some years where the populations appear to behave in concert:
years 1997, 2001, and 2007 have consistently low survival across all populations 
(i.e. <5\%, Fig.~\ref{fig:s1-dual}) and little variation across populations.
Our results also show that variation of survival in first year at sea is the most
important factor determining variation in number of returns, and suggests that 
changes in abundance are primarily driven by changes in marine survival. 
Nonetheless, variation in number of out-migrating smolts, and for some populations
variation in probability of returning after one winter at sea, also explain
variation in returns and thus contribute to the observed variation in return abundances.
Furthermore, the negative correlation between marine survival and smolt
abundances in some populations is suggestive of density-dependent processes
occurring at sea.
We could not assess trends for survival in the second winter at sea (\St) or
proportion returning as grilse (\Pg), as these parameter estimates were highly
uncertain and were strongly influenced by the priors.

% Perhaps there is a need to rethink
% our understanding of Atlantic salmon population dynamics in light of the
% possibilities that (1) any real and persistent declines in marine survival
% have been experienced by some but not necessarily all populations, (2)
% reductions in survival might have occurred over a relatively brief period of
% time and have not persisted, (3) marine survival has been relatively stable,
% or increasing in some populations for one or more decades, (4) variation in
% survival at the population level can be large even within a region.

% 2. How they compare to other publications
% Population vs regional trends 
At first glance, the large variation in marine survival trends among the seven
populations examined in our study seems to be at odds with the synchronous
trends of declining marine survival detected at broad regional scales
\citep{Olmos2019}. However, these two observations are not necessarily mutually
exclusive: our study is only a small subsample of the populations in the region,
and, with one exception, over a much shorter period of time,
and highly variable trends in marine survival among populations can still add
up to overall negative trends at a regional scale.
Aside from the overarching difference in the spatial scale of data sources
(i.e. river vs province scales), the divergence in local versus regional
trends could be further confounded by differences in model structure, such as
the methodology for estimating covariance, and use stock-recruitment
relationships rather than empirical smolt count estimates to estimate marine
survival.
% As trends in marine survival during the first winter at sea are highly
% independent among rivers on relatively small spatial scale, 
Our results suggest that trends from broader geographical areas (i.e.
province, state, or country-wide estimates) may not be representative of
individual populations, and concomitantly, trends of individual populations
may also not be representative of region-wide trends.

% Trends in survival at the population level
Trends in marine survival
among populations were compared by \citet{Chaput2012a} using adult return rates.
He found that for 4 of 6 populations examined, return rates in the 1990s 
were lower than those during the 1970s.
\citet{Gibson2016} calculated higher return rates of 2SW for the Nashwaak in
the 1970s than in the period since, with return rates of 1SW in the 1970s
being comparable to those in the late 2000s.
\citet{Friedland1993} compared return rates for a number of populations in eastern
North America between 1973 and 1988, and suggested there are similar trends among these. 
However, the similarity in these trends was driven primarily by two years, 1977 and 1978, which
show concurrent low and high relative return rates across populations,
respectively. Other years are much more variable relative to each other.
\citeauthor{Friedland1993}'s \citeyear{Friedland1993} time series ends in  
1988; thus there are only a few years for which to assess overlap with the
time series in our study.
While declines in return rates since the 1970s seem to be consistent among
populations, we were unable to assess if marine survival estimates were also
higher in the 1970s as we lacked data from this decade.
\citet{Dempson2003} described a general declining trend in marine survival for
Newfoundland populations (except WAB); we drew the same conclusion for Conne
River but not Campbellton River or WAB. It is not possible to draw broader
conclusions with data from only three Newfoundland populations, but it seems
that among index rivers, those in northern Newfoundland are among those with
the highest marine survival rates.

% Return rates vs marine survival estimates
In any event, we caution that the pooling of adult return rates
\citep{Chaput2012a, Friedland1993,Gibson2016} can mask inter-annual
variation in marine survival \citep{Hubley2011}, and hence might not produce
an accurate depiction of marine survival trends.
While river-specific return rate estimates are available for the populations
used in this study \citep{ICES2019}, these estimates are only an approximation
of marine survival with varying degrees of similarity depending on each
population's life histories. The estimates of return rates of one sea-winter salmon
approximate marine survival in the first year at sea for one
sea-winter-dominated populations, particularly for years in which 
directed marine fisheries are largely non-existent,
and we see this by comparing the three NL populations
with the return rates presented in \citet{ICES2019}. However, as the proportion of fish that
return as one sea-winter decreases, marine survival in the first year at sea
can increasingly diverge from return rates. Thus, trends in return rate
would be particularly misleading if the proportion returning as one sea-winter
varies in time;
proportion returning as one sea-winter was in important factor driving number of 
1SW returns in three of the populations examined (Fig.~\ref{fig:mu-rsq}).
Furthermore, return rates of two sea-winter fish also include survival in the
first winter at sea and the proportion returning as two sea-winter, thus
providing a very coarse estimate of marine survival in the second year at sea. 
As changes in return rates of two sea-winter fish are a result of a
combination of changes in survival in the first year at sea in the year prior,
survival in the second year at sea, and in the proportion returning as two
sea-winter, an increase in any of those parameters while the others remain
the same will result in an increase in return rates. Our model attempts to
improve some of the shortcomings of using return rates as a proxy of marine
survival by directly estimating marine survival in the first and second years
at sea, as well as the proportion returning as 1SW.

Interestingly, our estimates of survival in both first and second years at sea
for the Trinit\'{e} population are very similar to those produced by
\citet{Chaput2003b} using a two sex model, and our trends are almost identical
for the overlapping time period that marine survival was estimated for in
their study (1984-1998). While \citet{Chaput2003b} separated abundance data
for males and females based on sex ratio information and assumed their
survival rates were the same (to be able to reach an analytical solution), our
study reached almost the same results (albeit with slightly higher
uncertainty), using a Bayesian approach with informative priors. These
overlapping trends obtained with two different methods suggest that our method
is indeed effective at estimating marine survival.

% 3. Potential drivers of patterns 
There are a variety of potential explanations for the highly variable trends
in estimates marine survival in the first winter at sea.
Environmental drivers of survival (e.g., temperature, predation, prey abundance, 
interactions with farmed salmon) could be highly localized 
relative to broader-scale, even ocean-wide, drivers.
A recent study showed that correlations between oceanic temperature, primary
productivity, and post smolt survival of Atlantic salmon in the North Atlantic
are better explained by broad-scale environmental trends than regional ones
\citep{Olmos2020}.
However these local drivers are potentially much more difficult to quantify than 
broader ones.
% The synchrony reported for marine survival trends at broader spatial 
% scales \citep{Massiot-Granier2014,Olmos2019} might be attributable to the 
% use of stock-recruitment relationships to estimate survival,
% relationships that may have been confounded by changes in recruitment dynamics.
There is some evidence of a correlation between return rate and growth (as
indicated by inter-circuli spacing on scales), where years of poor growth
tended to also be years of poor survival \citep{Friedland1993}, supporting the
idea that marine survival is mediated by environmentally-driven changes in growth.
Furthermore, among European salmon, there is evidence of a positive correlation
between spring temperature in the Norwegian and North Seas and population abundance, 
suggesting warmer
conditions favour post-smolts \citep{Friedland1998}, based on mapping the
extent of area of suitable temperature (7-13 \textdegree C).

@@

@@

Egg-to-smolt survival in Atlantic salmon is highly variable, and perhaps more so
than marine survival \citep{Klemetsen2003,Chaput2015}.
While this variation is likely attributable to changes in freshwater
conditions (e.g. discharge, temperature, water quality) and uncertainty in
spawner and smolt estimates, 
changes in the oceanic conditions that spawners experience could also be
contributing to this variation.
Nonetheless, our results suggests that while variation in number of smolts was 
important for number of returns, it was considerable less important than
survival the first year at sea, which is indicative that return abundances 
are most strongly influenced by the marine phase of their life cycle.
Obviously, there would be a time lag (perhaps as much as a generation) in how such effects
might be manifest at the adult stage.
However, given that most correlations are between relatively monotonic declines
in abundance coupled also monotonic increases in climatic indices
over decadal time scales \citep[e.g.,][]{Friedland1998, Todd2008,
    Beaugrand2012}, it would be expected that these correlations would be
maintained even if salmon abundances were lagged by a generation length.

While there is little evidence that marine survival is density-dependent in
Atlantic salmon \citep{Jonsson1998,Gibson2006}, there could potentially be
some density-dependent processes during parts of the marine phase, 
particularly for populations that are likely to be subjected to
declining per capita population growth rates ($r$) generated by Allee effects.
While the correlations between return estimates and survival were negative for 
some populations (Fig.~\ref{fig:cor-params})
indicate that there may be some compensatory density dependent effects in the 
marine phase, our analysis provide no evidence of Allee effects.
Exploring relationships between survival and population size could potentially
shed light about the processes that have caused many of the population
declines that have been documented.

@@

Secondly, the assumed hierarchical structure might not be the most appropriate
for modelling smolt abundances. This approach results in shrinkage to the
mean, which means that the variation in annual smolt estimates is less than
it would be if not modelled hierarchically. 
That said, this assumption is likely to result in more conservative trends in
marine survival, as the variation is smolt estimates is reduced.
This shrinkage of annual smolt abundances is also reducing the $R^2$ values 
between smolts and estimates returns, albeit only marginally.
It is important to note that the hierarchical structure in the estimation of
\Pg seems like a reasonable assumption given that the probability of returning
as grilse has a genetic component associated to it \citep{Aykanat2019} and is
not expected to vary much, within a population, among years.
